---
title: "Bias Calculations of the Thesis Experiments"
author: "Utku Turk"
date: "`r Sys.Date()`"
output:
  rmdformats::html_docco:
    highlight: kate
    fig_height: 7
    fig_weight: 6
---

```{r setup, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)
library(fst) # for reading data files
library(magrittr) # for pipes
library(dplyr)
library(ggplot2)
library(formatR)
theme_set(theme_bw())
library(patchwork)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r readData}
data_ungrammaticalityBias <- read_fst("exp1_ungrammatical_bias.fst")
data_grammaticalityBias <- read_fst("exp2_grammatical_bias.fst")
data_ungrammaticalityBias$subject <- 
  paste0(data_ungrammaticalityBias$subject, 
         "_",
         data_ungrammaticalityBias$exp_bias)
data_grammaticalityBias$subject <- 
  paste0(data_grammaticalityBias$subject, 
         "_",
         data_grammaticalityBias$exp_bias)
df_all <- full_join(data_ungrammaticalityBias, data_grammaticalityBias)
```

```{r prepareData}
##  for filler analysis
data_ungrammaticalityBias_nonna_fillers <- 
  data_ungrammaticalityBias %>% 
    subset(!is.na(response_yes) & experiment == "filler")

data_grammaticalityBias_nonna_fillers <- 
  data_grammaticalityBias %>% 
    subset(!is.na(response_yes) & experiment == "filler")


df <- full_join(data_grammaticalityBias_nonna_fillers, data_ungrammaticalityBias_nonna_fillers)


# ##  for "whole" analysis
# data_ungrammaticalityBias_nonna <- 
#   data_ungrammaticalityBias %>% 
#     subset(!is.na(response_yes))
# 
# data_grammaticalityBias_nonna <- 
#   data_grammaticalityBias %>% 
#     subset(!is.na(response_yes))

```

<center>

## Formula Used

$c = - \frac{Z(Hit\ Rate)\ +\ Z(False\ Alarm\ Rate)}{2}$

Negative c implies bias towards grammatical responses

Positive c implies bias towards ungrammatical responses

Maybe I should add bayesian t-test results?

</center>

## Filler Only Bias Calculation

```{r prepareVariablesANDcalculateBiasforUNGFILLERS}
##  Fillers - Ung Bias
###  hit rates
hitRates <-
df %>% 
  group_by(subject) %>% 
    filter(exp_condition == "filler_g") %>% 
      summarize(
        hitRate =  mean(ResponseCorrect),
      ) 

###  false alarms
falseAlarms <-
df %>% 
  group_by(subject) %>% 
    filter(exp_condition == "filler_ung") %>% 
      summarize(
        falseAlarm =  mean(response_yes),
      ) 


###  start working on zscore dataframe
zscores <- 
  full_join(hitRates, 
            falseAlarms, 
            by = "subject")

### zscore calculation
zscores <- 
  zscores %>% 
            mutate(
              zscore_hitRates = (hitRate - mean(hitRate))/sd(hitRate),
              zscore_falseAlarms = (falseAlarm - mean(falseAlarm))/sd(falseAlarm)
            )

### bias calculation
biases <- 
  zscores %>% 
    mutate(
      bias = -1 * ( ( zscore_hitRates + zscore_falseAlarms ) / 2 )
    )

```

### By Participant Bias 

```{r plot_byPart_Bias, options}
biases %>% ggplot(aes(bias, subject)) + 
  geom_point() +
  xlab("c (bias) value") +
  ylab("Subject ID") + 
  ggtitle("By Participant Bias Values\n using Fillers for Ungrammatical Bias Exp") +
  theme_bw()
```


<!-- ### EXP 1 - Bias Towards Ungrammaticality -->

<!-- ```{r plot1} -->


<!-- biases_ung_fillers %>% ggplot(aes(bias, subject)) +  -->
<!--   geom_point() + -->
<!--   xlab("c (bias) value") + -->
<!--   ylab("Subject ID") +  -->
<!--   ggtitle("By Participant Bias Values\n using Fillers for Ungrammatical Bias Exp") + -->
<!--   theme_bw() -->

<!-- ``` -->


-   Participants with `_ungrammatical` were told "Most of the items are UNGRAMMATICAL."
-   Participants with `_grammatical` were told "Most of the items are GRAMMATICAL."
-   Previous results showed that this manipulation did not was not successful and as can be seen from this graph, they are mostly centered around 0. 
-   Seems like on average participants were mostly unbiased.

\noindent **Question:** Even though I failed to introduce any bias, Participants that are grouped according to their bias value should reflect the predictions nevertheless.

-   So, I cut the participants into two groups.
-   Participants (N= `r sum(biases$bias) > 0`) who had above-zero value of c are biased towards ungrammatical answers.
-   Participants (N= `r sum(biases$bias) < 0`) who had below-zero value of c are biased towards grammatical answers.


<!--     -   Number of Participants above 0  = `r  sum(biases_ung_fillers$bias > 0)` -->
<!--     -   Number of Participants above 0.1 = `r  sum(biases_ung_fillers$bias > 0.1)` -->
<!--     -   Number of Participants above 0.2 = `r  sum(biases_ung_fillers$bias > 0.2)` -->
<!--     -   Number of Participants above 0.4 = `r  sum(biases_ung_fillers$bias > 0.4)` -->
<!--     -   Number of Participants above 0.5 = `r  sum(biases_ung_fillers$bias > 0.5)` -->

<!-- -   (Biased towards Grammatical Answers) -->

<!--     -   Number of Participants below 0  = `r  sum(biases_ung_fillers$bias < 0)` -->
<!--     -   Number of Participants below 0.1 = `r  sum(biases_ung_fillers$bias < -0.1)` -->
<!--     -   Number of Participants below 0.2 = `r  sum(biases_ung_fillers$bias < -0.2)` -->
<!--     -   Number of Participants below 0.4 = `r  sum(biases_ung_fillers$bias < -0.4)` -->
<!--     -   Number of Participants below 0.5 = `r  sum(biases_ung_fillers$bias < -0.5)` -->

<!-- -   (Unbiased Population) -->

<!--     -   Number of Participants at exact 0  = `r  sum(biases_ung_fillers$bias = 0)` -->
<!--     -   Number of Participants between -0.1 and 0.1  = `r  sum(biases_ung_fillers$bias < 0.1 & biases_ung_fillers$bias > -0.1)` -->
<!--     -   Number of Participants between -0.2 and 0.2  = `r  sum(biases_ung_fillers$bias < 0.2 & biases_ung_fillers$bias > -0.2)` -->
<!--     -   Number of Participants between -0.4 and 0.4  = `r  sum(biases_ung_fillers$bias < 0.4 & biases_ung_fillers$bias > -0.4)` -->
<!--     -   Number of Participants between -0.5 and 0.5  = `r  sum(biases_ung_fillers$bias < 0.5 & biases_ung_fillers$bias > -0.5)` -->

<!-- -   Question of where to cut the cake? -->

<!--     -   Choosing 0 seems like easy way out. -->
<!--     -   Choosing 0.2 seems like a better distribution. -->




<!-- ```{r prepareVariablesANDcalculateBiasforGFILLERS} -->
<!-- ##  Fillers - Gram Bias -->
<!-- ###  hit rates -->
<!-- hitRates_g_fillers <- -->
<!--   data_grammaticalityBias_nonna_fillers %>%  -->
<!--   group_by(subject) %>%  -->
<!--   filter(exp_condition == "filler_g") %>%  -->
<!--   summarize( -->
<!--     hitRate =  mean(ResponseCorrect), -->
<!--   ) -->

<!-- ### false alarms -->
<!-- falseAlarms_g_fillers <- -->
<!--   data_grammaticalityBias_nonna_fillers %>%  -->
<!--   group_by(subject) %>%  -->
<!--   filter(exp_condition == "filler_ung") %>%  -->
<!--   summarize( -->
<!--     falseAlarm =  mean(response_yes), -->
<!--   )  -->

<!-- ###  start working on zscore dataframe -->
<!-- zscores_g_fillers <-  -->
<!--   full_join(hitRates_g_fillers,  -->
<!--             falseAlarms_g_fillers,  -->
<!--             by = "subject") -->

<!-- ### zscore calculation -->
<!-- zscores_g_fillers <-  -->
<!--   zscores_g_fillers %>%  -->
<!--     mutate( -->
<!--       zscore_hitRates = (hitRate - mean(hitRate))/sd(hitRate), -->
<!--       zscore_falseAlarms = (falseAlarm - mean(falseAlarm))/sd(falseAlarm) -->
<!--     ) -->

<!-- ### bias calculation -->
<!-- biases_g_fillers <-  -->
<!--   zscores_g_fillers %>%  -->
<!--     mutate( -->
<!--       bias = -1 * ((zscore_hitRates + zscore_falseAlarms)/2) -->
<!--     ) -->

<!-- ``` -->

<!-- ### EXP 2 - Bias Towards Grammatical Answers -->

<!-- ```{r plot2} -->
<!-- ### plot -->
<!-- biases_g_fillers %>% ggplot(aes(bias, subject)) +  -->
<!--   geom_point() + -->
<!--   xlab("c (bias) value") + -->
<!--   ylab("Subject ID") +  -->
<!--   ggtitle("By Participant Bias Values\n using Fillers for Grammatical Bias Exp") + -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- -   Participants were told "Most of the items are GRAMMATICAL." -->
<!-- -   Seems like on average participants were mostly unbiased. -->
<!-- -   In the same experiments, we have 3 types of people: unbiased, biased towards ungrammatical and grammatical -->
<!-- -   (Biased towards Ungrammatical Answers) -->

<!--     -   Number of Participants above 0  = `r  sum(biases_g_fillers$bias > 0)` -->
<!--     -   Number of Participants above 0.1 = `r  sum(biases_g_fillers$bias > 0.1)` -->
<!--     -   Number of Participants above 0.2 = `r  sum(biases_g_fillers$bias > 0.2)` -->
<!--     -   Number of Participants above 0.4 = `r  sum(biases_g_fillers$bias > 0.4)` -->
<!--     -   Number of Participants above 0.5 = `r  sum(biases_g_fillers$bias > 0.5)` -->

<!-- -   (Biased towards Grammatical Answers) -->

<!--     -   Number of Participants below 0  = `r  sum(biases_g_fillers$bias < 0)` -->
<!--     -   Number of Participants below 0.1 = `r  sum(biases_g_fillers$bias < -0.1)` -->
<!--     -   Number of Participants below 0.2 = `r  sum(biases_g_fillers$bias < -0.2)` -->
<!--     -   Number of Participants below 0.4 = `r  sum(biases_g_fillers$bias < -0.4)` -->
<!--     -   Number of Participants below 0.5 = `r  sum(biases_g_fillers$bias < -0.5)` -->

<!-- -   (Unbiased Population) -->

<!--     -   Number of Participants at exact 0  = `r  sum(biases_g_fillers$bias = 0)` -->
<!--     -   Number of Participants between -0.1 and 0.1  = `r  sum(biases_g_fillers$bias < 0.1 & biases_g_fillers$bias > -0.1)` -->
<!--     -   Number of Participants between -0.2 and 0.2  = `r  sum(biases_g_fillers$bias < 0.2 & biases_g_fillers$bias > -0.2)` -->
<!--     -   Number of Participants between -0.4 and 0.4  = `r  sum(biases_g_fillers$bias < 0.4 & biases_g_fillers$bias > -0.4)` -->
<!--     -   Number of Participants between -0.5 and 0.5  = `r  sum(biases_g_fillers$bias < 0.5 & biases_g_fillers$bias > -0.5)` -->

<!-- -   Question of where to cut the cake? Againm, choosing 0.2 seems like a better distribution. Especially when looked at both of the experiments. Check out the histograms. The one in the left is for the Exp 1, the right one is for the Exp 2.  -->



<!-- ```{r exp1Histograms, fig.width=15, fig.height=7, warning=FALSE, message=FALSE} -->
<!-- hist_ung_participants <- ggplot(data=biases_ung_fillers, aes(bias)) + geom_histogram()+ scale_x_continuous(breaks=seq(-2.5, 2.5, 0.5)) -->
<!-- hist_g_participants <- ggplot(data=biases_g_fillers, aes(bias)) + geom_histogram() + scale_x_continuous(breaks=seq(-2.5, 2.5, 0.5)) -->

<!-- hist_ung_participants + hist_g_participants -->

<!-- ``` -->


<!-- -   Commented out bias on average plots as well.  -->

<!-- ```{r ExpWidePrepandPlot} -->
<!-- ## Exp-wide data -->

<!-- ### prepare means and CI -->
<!-- ungBias_fillers_ExpBias <-  -->
<!--   biases_ung_fillers %>%   -->
<!--     summarize(p_bias = mean(bias),  -->
<!--             N = length(subject), -->
<!--             CI = 1.96*(sd(bias)/sqrt(length(bias))))  -->

<!-- ungBias_fillers_ExpBias$exp <- "ungBias" -->

<!-- gBias_fillers_ExpBias <-  -->
<!--   biases_g_fillers %>%   -->
<!--     summarize(p_bias = mean(bias),  -->
<!--               N = length(subject), -->
<!--               CI = 1.96*(sd(bias)/sqrt(length(bias))))  -->

<!-- gBias_fillers_ExpBias$exp <- "gBias" -->

<!-- ### binding -->
<!-- filler_biases <- -->
<!--   rbind(gBias_fillers_ExpBias,  -->
<!--         ungBias_fillers_ExpBias) -->

<!-- ``` -->

<!-- ```{r plot3} -->
<!-- ### plot -->
<!-- filler_biases %>% -->
<!--   ggplot(aes(exp, p_bias)) + -->
<!--   geom_point() + -->
<!--   geom_errorbar(aes(ymin = p_bias-CI, -->
<!--                     ymax = p_bias+CI)) + -->
<!--   xlab("") + -->
<!--   scale_x_discrete( -->
<!--     labels = c("Grammatical Bias", -->
<!--                "Ungrammatical Bias") -->
<!--   ) + -->
<!--   ylab("Mean c Value") + -->
<!--   ggtitle("Mean Bias and 95% CIs\n using filler items") + -->
<!--   theme_bw() -->
<!-- ``` -->



<!-- ## Whole Experiment Bias Calculation -->


<!-- -   Commented out the part where we analyze the bias using the whole experiment as they did in Hammerly et al. -->
<!-- ```{r UNGwholeBias} -->
<!-- ##  Whole - Ung Bias -->

<!-- hitRates_ung_whole <- -->
<!--   data_ungrammaticalityBias_nonna %>% -->
<!--   group_by(subject) %>% -->
<!--   filter(grammatical == "gram") %>% -->
<!--   summarize( -->
<!--     hitRate =  mean(ResponseCorrect), -->
<!--   ) -->

<!-- falseAlarms_ung_whole <- -->
<!--   data_ungrammaticalityBias_nonna %>% -->
<!--   group_by(subject) %>% -->
<!--   filter(grammatical == "ungram") %>% -->
<!--   summarize( -->
<!--     falseAlarm =  mean(response_yes), -->
<!--   ) -->

<!-- zscores_ung_whole <- -->
<!--   full_join(hitRates_ung_whole, -->
<!--             falseAlarms_ung_whole, by = "subject") -->

<!-- zscores_ung_whole <- zscores_ung_whole %>% -->
<!--   mutate( -->
<!--     zscore_hitRates = (hitRate - mean(hitRate))/sd(hitRate), -->
<!--     zscore_falseAlarms = (falseAlarm - mean(falseAlarm))/sd(falseAlarm) -->
<!--   ) -->

<!-- biases_ung_whole <- zscores_ung_whole %>% -->
<!--   mutate( -->
<!--     bias = -1 * ((zscore_hitRates + zscore_falseAlarms)/2) -->
<!--   ) -->

<!-- ``` -->

<!-- ```{r plot4} -->
<!-- biases_ung_whole %>% ggplot(aes(bias, subject)) +  -->
<!--   geom_point()+ -->
<!--   xlab("c (bias) value") + -->
<!--   ylab("Subject ID") +  -->
<!--   ggtitle("By Participant Bias Values\n using All items for Ungrammatical Bias Exp") + -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- ```{r GwholeBias} -->
<!-- hitRates_g_whole <- -->
<!--   data_grammaticalityBias_nonna %>%  -->
<!--   group_by(subject) %>%  -->
<!--   filter(grammatical == "gram") %>%  -->
<!--   summarize( -->
<!--     hitRate =  mean(ResponseCorrect), -->
<!--   )  -->

<!-- falseAlarms_g_whole <- -->
<!--   data_grammaticalityBias_nonna %>%  -->
<!--   group_by(subject) %>%  -->
<!--   filter(grammatical == "ungram") %>%  -->
<!--   summarize( -->
<!--     falseAlarm =  mean(response_yes), -->
<!--   )  -->

<!-- zscores_g_whole <-  -->
<!--   full_join(hitRates_g_whole,  -->
<!--             falseAlarms_g_whole, by = "subject") -->

<!-- zscores_g_whole <- zscores_g_whole %>%  -->
<!--   mutate( -->
<!--     zscore_hitRates = (hitRate - mean(hitRate))/sd(hitRate), -->
<!--     zscore_falseAlarms = (falseAlarm - mean(falseAlarm))/sd(falseAlarm) -->
<!--   ) -->

<!-- biases_g_whole <- zscores_g_whole %>%  -->
<!--   mutate( -->
<!--     bias = -1 * ((zscore_hitRates + zscore_falseAlarms)/2) -->
<!--   ) -->


<!-- ``` -->

<!-- ```{r plot5} -->
<!-- biases_g_whole %>% ggplot(aes(bias, subject)) +  -->
<!--   geom_point() + geom_line()+ -->
<!--   xlab("c (bias) value") + -->
<!--   ylab("Subject ID") +  -->
<!--   ggtitle("By Participant Bias Values\n using All items for Grammatical Bias Exp") + -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- ```{r wideWholeBias} -->
<!-- ungBias_whole_ExpBias <-  -->
<!--   biases_ung_whole %>%   -->
<!--   summarize(p_bias = mean(bias),  -->
<!--             N = length(subject), -->
<!--             CI = 1.96*(sd(bias)/sqrt(length(bias))))  -->

<!-- ungBias_whole_ExpBias$exp <- "ungBias" -->

<!-- gBias_whole_ExpBias <-  -->
<!--   biases_g_whole %>%   -->
<!--   summarize(p_bias = mean(bias),  -->
<!--             N = length(subject), -->
<!--             CI = 1.96*(sd(bias)/sqrt(length(bias))))  -->

<!-- gBias_whole_ExpBias$exp <- "gBias" -->

<!-- whole_biases <- -->
<!--   rbind(gBias_whole_ExpBias, ungBias_whole_ExpBias) -->



<!-- ``` -->

<!-- ```{r plot7} -->

<!-- whole_biases %>%  -->
<!--   ggplot(aes(exp, p_bias)) +  -->
<!--   geom_point() +  -->
<!--   geom_errorbar(aes(ymin = p_bias-CI,  -->
<!--                     ymax = p_bias+CI)) + -->
<!--   xlab("") + -->
<!--   scale_x_discrete( -->
<!--     labels = c("Grammatical Bias", -->
<!--                "Ungrammatical Bias") -->
<!--   ) + -->
<!--   ylab("Mean c Value") +  -->
<!--   ggtitle("Mean Bias and 95% CIs\n using all items") + -->
<!--   theme_bw() -->

<!-- ``` -->



## Re-look at the Ungrammaticality Assymetry


-   Obviously, I failed to introduce any bias in any of the experiments. 
-   Two questions to ask:

    -   There is a clear difference between two experiments. Is this difference only about sampling?
    -   Even though introducing a bias failed, there are still people who were biased (either towards grammatical or ungrammatical) regardless of our experiment.
    -   These subgroups of participants should behave according to the predictions.
    
-   What are the predictions?
-   For Participants biased towards ungrammatical responses:
    
    -   RT-wise: Faster RTs in ungrammatical conditions.
    -   Response-wise: Ungrammaticality Effects, that is a substantial difference between grammatical-sg attractor and grammatical-pl attractor conditions.


<!-- ### Exp 1 and 2 when the bias is determined as above or below 0 -->


<!-- -   Commented out the part where we determine a two-way bias. Having a three-mode assumption for the participants seemed a bit more natural.     -->


<!-- ```{r labelParticipants accordingly} -->
<!-- # For ungrammatical bias -->
<!-- # using fillers -->
<!-- ## lets use  -->
<!-- biases_ung_fillers %<>% within(., { -->
<!--   Bias <- ifelse(bias <= 0, "towardsG", "towardsUng") -->
<!-- }) -->

<!-- biases_ung_fillers %<>% select(subject, Bias) -->

<!-- biases_ung_whole %<>% within(., { -->
<!--   BiasWhole <- ifelse(bias <= 0, "towardsG", "towardsUng") -->
<!-- }) -->

<!-- biases_ung_whole %<>% select(subject, BiasWhole) -->

<!-- data_ungrammaticalityBias_nonna  %<>%  -->
<!--   full_join(.,  -->
<!--             biases_ung_fillers,  -->
<!--             by = "subject") -->

<!-- data_ungrammaticalityBias_nonna  %<>%  -->
<!--   full_join(.,  -->
<!--             biases_ung_whole,  -->
<!--             by = "subject") -->



<!-- exp1_towardsG <- data_ungrammaticalityBias_nonna %>% filter(Bias == "towardsG") -->
<!-- avg_clean <- list() -->
<!-- avg_clean$resp <- exp1_towardsG %>%  -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = TRUE) -->
<!--   }) -->

<!-- avg_clean$rt_correct <- exp1_towardsG %>% subset(ResponseCorrect) %>% -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = RT,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = FALSE) -->
<!--   }) -->

<!-- avg_exp <- avg_clean %>%  -->
<!--   lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") }) -->

<!-- pd <- position_dodge(0.0) -->
<!-- p_avg_resp <- avg_exp$resp %>% -->
<!--   ggplot(aes(grammatical, M, #linetype = attractor_num,  -->
<!--              color = attractor_num, group = attractor_num)) +  -->
<!--   geom_point(position = pd) + geom_line(position = pd) -->

<!-- p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd) -->

<!-- # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) +  -->
<!-- #                             geom_point(data = avg_fillers) +  -->

<!-- p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) + -->
<!--   theme_bw() + xlab("") + ylab("Percentage 'acceptable'") -->
<!-- p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1)) -->
<!-- p_avg_resp <- p_avg_resp + theme_bw() -->
<!-- p_avg_resp_exp1_towardsG <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) +  -->
<!--   scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) +  -->
<!--   theme(text = element_text(size = 20)) -->


<!-- ############ -->

<!-- exp1_towardsUng <- data_ungrammaticalityBias_nonna %>% filter(Bias == "towardsUng") -->
<!-- avg_clean <- list() -->
<!-- avg_clean$resp <- exp1_towardsUng %>%  -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = TRUE) -->
<!--   }) -->

<!-- avg_clean$rt_correct <- exp1_towardsUng %>% subset(ResponseCorrect) %>% -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = RT,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = FALSE) -->
<!--   }) -->

<!-- avg_exp <- avg_clean %>%  -->
<!--   lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") }) -->

<!-- pd <- position_dodge(0.0) -->
<!-- p_avg_resp <- avg_exp$resp %>% -->
<!--   ggplot(aes(grammatical, M, #linetype = attractor_num,  -->
<!--              color = attractor_num, group = attractor_num)) +  -->
<!--   geom_point(position = pd) + geom_line(position = pd) -->

<!-- p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd) -->

<!-- # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) +  -->
<!-- #                             geom_point(data = avg_fillers) +  -->

<!-- p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) + -->
<!--   theme_bw() + xlab("") + ylab("Percentage 'acceptable'") -->
<!-- p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1)) -->
<!-- p_avg_resp <- p_avg_resp + theme_bw() -->
<!-- p_avg_resp_exp1_towardsUng <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) +  -->
<!--   scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) +  -->
<!--   theme(text = element_text(size = 20)) -->


<!-- ``` -->

<!-- ```{r plotsforExp1, fig.width=15} -->
<!-- library(patchwork) -->
<!-- p_avg_resp_exp1_towardsUng + p_avg_resp_exp1_towardsG -->
<!-- ``` -->

<!-- ```{r exp2} -->

<!-- # For ungrammatical bias -->
<!-- # using fillers -->
<!-- ## lets use  -->
<!-- biases_g_fillers %<>% within(., { -->
<!--   Bias <- ifelse(bias <= 0, "towardsG", "towardsUng") -->
<!-- }) -->

<!-- biases_g_fillers %<>% select(subject, Bias) -->

<!-- biases_g_whole %<>% within(., { -->
<!--   BiasWhole <- ifelse(bias <= 0, "towardsG", "towardsUng") -->
<!-- }) -->

<!-- biases_g_whole %<>% select(subject, BiasWhole) -->

<!-- data_grammaticalityBias_nonna  %<>%  -->
<!--   full_join(.,  -->
<!--             biases_g_fillers,  -->
<!--             by = "subject") -->

<!-- data_grammaticalityBias_nonna  %<>%  -->
<!--   full_join(.,  -->
<!--             biases_g_whole,  -->
<!--             by = "subject") -->



<!-- exp2_towardsG <- data_grammaticalityBias_nonna %>% filter(Bias == "towardsG") -->
<!-- avg_clean <- list() -->
<!-- avg_clean$resp <- exp2_towardsG %>%  -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = TRUE) -->
<!--   }) -->

<!-- avg_clean$rt_correct <- exp2_towardsG %>% subset(ResponseCorrect) %>% -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = RT,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = FALSE) -->
<!--   }) -->

<!-- avg_exp <- avg_clean %>%  -->
<!--   lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") }) -->

<!-- pd <- position_dodge(0.0) -->
<!-- p_avg_resp <- avg_exp$resp %>% -->
<!--   ggplot(aes(grammatical, M, #linetype = attractor_num,  -->
<!--              color = attractor_num, group = attractor_num)) +  -->
<!--   geom_point(position = pd) + geom_line(position = pd) -->

<!-- p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd) -->

<!-- # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) +  -->
<!-- #                             geom_point(data = avg_fillers) +  -->

<!-- p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) + -->
<!--   theme_bw() + xlab("") + ylab("Percentage 'acceptable'") -->
<!-- p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1)) -->
<!-- p_avg_resp <- p_avg_resp + theme_bw() -->
<!-- p_avg_resp_exp2_towardsG <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) +  -->
<!--   scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) +  -->
<!--   theme(text = element_text(size = 20)) -->


<!-- ############ -->

<!-- exp2_towardsUng <- data_grammaticalityBias_nonna %>% filter(Bias == "towardsUng") -->
<!-- avg_clean <- list() -->
<!-- avg_clean$resp <- exp2_towardsUng %>%  -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = TRUE) -->
<!--   }) -->

<!-- avg_clean$rt_correct <- exp2_towardsUng %>% subset(ResponseCorrect) %>% -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = RT,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = FALSE) -->
<!--   }) -->

<!-- avg_exp <- avg_clean %>%  -->
<!--   lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") }) -->

<!-- pd <- position_dodge(0.0) -->
<!-- p_avg_resp <- avg_exp$resp %>% -->
<!--   ggplot(aes(grammatical, M, #linetype = attractor_num,  -->
<!--              color = attractor_num, group = attractor_num)) +  -->
<!--   geom_point(position = pd) + geom_line(position = pd) -->

<!-- p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd) -->

<!-- # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) +  -->
<!-- #                             geom_point(data = avg_fillers) +  -->

<!-- p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) + -->
<!--   theme_bw() + xlab("") + ylab("Percentage 'acceptable'") -->
<!-- p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1)) -->
<!-- p_avg_resp <- p_avg_resp + theme_bw() -->
<!-- p_avg_resp_exp2_towardsUng <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) +  -->
<!--   scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) +  -->
<!--   theme(text = element_text(size = 20)) -->



<!-- ``` -->

<!-- ```{r plotsforExp2, fig.width=15} -->
<!-- library(patchwork) -->
<!-- p_avg_resp_exp2_towardsUng + p_avg_resp_exp2_towardsG -->
<!-- ``` -->





### Exp 1 and 2 when theBias is determined as below -0.2 or above 0.2


```{r labelParticipants accordingly}
# For ungrammatical bias
# using fillers
## lets use 
biases %<>% within(., {
  Bias <- ifelse(bias < 0, "towardsG", 
                 "towardsUng"
          )
})

bias_df <- biases %>% select(subject, Bias)


df_all  %<>% 
  full_join(., 
            bias_df, 
            by = "subject")



towardsG <- df_all %>% filter(Bias == "towardsG")
avg_clean <- list()
avg_clean$resp <- towardsG %>% 
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = TRUE)
  })

avg_clean$rt_correct <- towardsG %>% subset(ResponseCorrect) %>%
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = FALSE)
  })

avg_exp <- avg_clean %>% 
  lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") })

pd <- position_dodge(0.0)
p_avg_resp <- avg_exp$resp %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp <- p_avg_resp + theme_bw()
p_avg_resp_towardsG <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20))


############

towardsUng <- df_all %>% filter(Bias == "towardsUng")
avg_clean2 <- list()
avg_clean2$resp <- towardsUng %>% 
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = TRUE)
  })

avg_clean2$rt_correct <- towardsUng %>% subset(ResponseCorrect) %>%
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = FALSE)
  })

avg_exp2 <- avg_clean2 %>% 
  lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") })

pd <- position_dodge(0.0)
p_avg_resp2 <- avg_exp2$resp %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_avg_resp2 <- p_avg_resp2 + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp2 <- p_avg_resp2 + theme_bw()
p_avg_resp_towardsUng <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20))


```

```{r plotsforExp1, fig.width=15}
library(patchwork)
p_avg_resp_towardsUng + p_avg_resp_towardsG
```



<!-- ```{r 3wayexp2} -->

<!-- # For ungrammatical bias -->
<!-- # using fillers -->
<!-- ## lets use  -->
<!-- biases_g_fillers %<>% within(., { -->
<!--   Bias <- ifelse(bias <= -0.2, "towardsG",  -->
<!--                  ifelse( -->
<!--                    bias >= 0.2, "towardsUng", "NonBias" -->
<!--                  ) -->
<!--           ) -->
<!-- }) -->

<!-- biases_g_fillers_selected <- biases_g_fillers %>% select(subject, Bias) -->

<!-- biases_g_whole %<>% within(., { -->
<!--   BiasWhole <- ifelse(bias <= -0.2, "towardsG",  -->
<!--                  ifelse( -->
<!--                    bias >= 0.2, "towardsUng", "NonBias" -->
<!--                  ) -->
<!--           ) -->
<!-- }) -->

<!-- biases_g_whole_selected <- biases_g_whole %>% select(subject, BiasWhole) -->

<!-- data_grammaticalityBias_nonna  %<>%  -->
<!--   full_join(.,  -->
<!--             biases_g_fillers,  -->
<!--             by = "subject") -->

<!-- data_grammaticalityBias_nonna  %<>%  -->
<!--   full_join(.,  -->
<!--             biases_g_whole,  -->
<!--             by = "subject") -->



<!-- exp2_towardsG <- data_grammaticalityBias_nonna %>% filter(Bias == "towardsG") -->
<!-- avg_clean <- list() -->
<!-- avg_clean$resp <- exp2_towardsG %>%  -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = TRUE) -->
<!--   }) -->

<!-- avg_clean$rt_correct <- exp2_towardsG %>% subset(ResponseCorrect) %>% -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = RT,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = FALSE) -->
<!--   }) -->

<!-- avg_exp <- avg_clean %>%  -->
<!--   lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") }) -->

<!-- pd <- position_dodge(0.0) -->
<!-- p_avg_resp <- avg_exp$resp %>% -->
<!--   ggplot(aes(grammatical, M, #linetype = attractor_num,  -->
<!--              color = attractor_num, group = attractor_num)) +  -->
<!--   geom_point(position = pd) + geom_line(position = pd) -->

<!-- p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd) -->

<!-- # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) +  -->
<!-- #                             geom_point(data = avg_fillers) +  -->

<!-- p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) + -->
<!--   theme_bw() + xlab("") + ylab("Percentage 'acceptable'") -->
<!-- p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1)) -->
<!-- p_avg_resp <- p_avg_resp + theme_bw() -->
<!-- p_avg_resp_exp2_towardsG <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) +  -->
<!--   scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) +  -->
<!--   theme(text = element_text(size = 20)) -->


<!-- ############ -->

<!-- exp2_towardsUng <- data_grammaticalityBias_nonna %>% filter(Bias == "towardsUng") -->
<!-- avg_clean <- list() -->
<!-- avg_clean$resp <- exp2_towardsUng %>%  -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = TRUE) -->
<!--   }) -->

<!-- avg_clean$rt_correct <- exp2_towardsUng %>% subset(ResponseCorrect) %>% -->
<!--   plyr::ddply(c("experiment"), function(df) { -->
<!--     df %>% se_cousineau(n_conditions = 4, subject, DV = RT,  -->
<!--                         group = c("experiment", "grammatical", "attractor_num"),  -->
<!--                         is_proportion = FALSE) -->
<!--   }) -->

<!-- avg_exp <- avg_clean %>%  -->
<!--   lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") }) -->

<!-- pd <- position_dodge(0.0) -->
<!-- p_avg_resp <- avg_exp$resp %>% -->
<!--   ggplot(aes(grammatical, M, #linetype = attractor_num,  -->
<!--              color = attractor_num, group = attractor_num)) +  -->
<!--   geom_point(position = pd) + geom_line(position = pd) -->

<!-- p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd) -->

<!-- # p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) +  -->
<!-- #                             geom_point(data = avg_fillers) +  -->

<!-- p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) + -->
<!--   theme_bw() + xlab("") + ylab("Percentage 'acceptable'") -->
<!-- p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1)) -->
<!-- p_avg_resp <- p_avg_resp + theme_bw() -->
<!-- p_avg_resp_exp2_towardsUng <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) +  -->
<!--   scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) +  -->
<!--   theme(text = element_text(size = 20)) -->



<!-- ``` -->

<!-- ```{r plotsforExp2, fig.width=15} -->
<!-- library(patchwork) -->
<!-- p_avg_resp_exp2_towardsUng + p_avg_resp_exp2_towardsG -->
<!-- ``` -->
