---
title: "Bias Calculations of the Thesis Experiments"
author: "Utku Turk"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
  highlight: kate
fig_height: 7
fig_weight: 6
---
  
```{r setup, echo=FALSE, cache=FALSE, message = FALSE}

#############################################
############### DO NOT KNIT #################
############### IMMEDIATELY #################
#############################################
############## CHECK PACKAGES ###############
################## AND ######################
############### INSTALL THEM ################
####### BY USING THE FUNCTION BELOW #########


## WRITE CRAN PACKAGES HERE
packages = c("knitr", 
             "rmdformats",
             "fst", 
             "magrittr", 
             "dplyr", 
             "brms", 
             "ggplot2",
             "formatR", 
             "patchwork", 
             "devtools",
             "rmdformats")

## Now load or install&load all
package.check <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  }
)
# This will fail real hard when we have packages from github


theme_set(theme_bw())
source("../scripts/misc.R")
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
               cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r readData}
data_ungrammaticalityBias <- read_fst("exp1_ungrammatical_bias.fst")
data_grammaticalityBias <- read_fst("exp2_grammatical_bias.fst")
data_ungrammaticalityBias$subject <- 
  paste0(data_ungrammaticalityBias$subject, 
         "_",
         data_ungrammaticalityBias$exp_bias)
data_grammaticalityBias$subject <- 
  paste0(data_grammaticalityBias$subject, 
         "_",
         data_grammaticalityBias$exp_bias)
df_all <- full_join(data_ungrammaticalityBias, data_grammaticalityBias)
```

```{r prepareData}
##  for filler analysis
data_ungrammaticalityBias_nonna_fillers <- 
  data_ungrammaticalityBias %>% 
  subset(!is.na(response_yes) & experiment == "filler")

data_grammaticalityBias_nonna_fillers <- 
  data_grammaticalityBias %>% 
  subset(!is.na(response_yes) & experiment == "filler")


df <- full_join(data_grammaticalityBias_nonna_fillers, data_ungrammaticalityBias_nonna_fillers)

```

# Answers to Question on OneNote

-   **Presence of Agreement Attraction in Both Groups?** 

    -   I will talk about groups **not** in the sense that participants from Exp 1 and Exp 2, but in the sense that participants who are biased towards grammatical or ungrammatical answers.
    -   Agreement Attractions (difference between plural and singular attractor conditions in ungrammatical sentences) exists for both groups.
    -   Though, the magnitutde differens. Ungrammatical Bias < Grammatical Bias.

-   **What is the bias situation?**

    -   Bias manipulation failed real hard. No effect of the instruction at all.
    -   The means and the CIs of the experiments are basically identical (Graph omitted here, will add in the next iteration).
    
-   **What happens when we compute bias independent of our manipulation?**

    -   We replicate the aggreement attraction effects in acceptability answers.
    -   RTs not completely. RTs of people who are biased towards Grammaticality resembles to "No Bias" situation more.
    -   **Note:** For "No Bias" situation, I just used all of the participants, which has a median of 0.6 for c value. CIs and the mean of the whole dataset is *basically* "No Bias" situation Hammerly et al. 
    -   The better way would be using our previous experiment where we do not introduce any bias. But theoretically this should hold as well. But it does not.

# Formula Used
  
$c = - \frac{Z(Hit\ Rate)\ +\ Z(False\ Alarm\ Rate)}{2}$
  
Negative c implies bias towards grammatical responses

Positive c implies bias towards ungrammatical responses

Maybe I should add bayesian t-test results?
  

  
# Filler Only Bias Calculation
  
```{r prepareVariablesANDcalculateBiasforUNGFILLERS}
##  Fillers - Ung Bias
###  hit rates
hitRates <-
  df %>% 
  group_by(subject) %>% 
  filter(exp_condition == "filler_g") %>% 
  summarize(
    hitRate =  mean(ResponseCorrect),
  ) 

###  false alarms
falseAlarms <-
  df %>% 
  group_by(subject) %>% 
  filter(exp_condition == "filler_ung") %>% 
  summarize(
    falseAlarm =  mean(response_yes),
  ) 


###  start working on zscore dataframe
zscores <- 
  full_join(hitRates, 
            falseAlarms, 
            by = "subject")

### zscore calculation
zscores <- 
  zscores %>% 
  mutate(
    zscore_hitRates = (hitRate - mean(hitRate))/sd(hitRate),
    zscore_falseAlarms = (falseAlarm - mean(falseAlarm))/sd(falseAlarm)
  )

### bias calculation
biases <- 
  zscores %>% 
  mutate(
    bias = -1 * ( ( zscore_hitRates + zscore_falseAlarms ) / 2 )
  )
cutpoint <- median(biases$bias)
```

## By Participant Bias 

```{r plot_byPart_Bias, fig.height=12, fig.width=15}
biases %>% ggplot(aes(bias, subject)) + 
  geom_point() +
  xlab("c (bias) value") +
  ylab("Subject ID") + 
  ggtitle("By Participant Bias Values\n using Fillers for Ungrammatical Bias Exp") +
  theme_bw() | ggplot(data=biases, aes(bias)) + geom_histogram()
```

  
-   Participants with `_ungrammatical` were told "Most of the items are UNGRAMMATICAL."
-   Participants with `_grammatical` were told "Most of the items are GRAMMATICAL."
-   Previous results showed that this manipulation did not was not successful and as can be seen from this graph, they are mostly centered around 0. 
-   Seems like on average participants were mostly unbiased.

__Question:__ Even though I failed to introduce any bias, Participants that are grouped according to their bias value should reflect the predictions nevertheless.

-   So, I cut the participants into two groups.
-   Participants (N= `r sum(biases$bias > cutpoint)`) who had above-median value of c  (`r round(cutpoint,2)`) are biased towards ungrammatical answers.
-   Participants (N= `r sum(biases$bias < cutpoint)`) who had below-median value of c (`r round(cutpoint,2)`) are biased towards grammatical answers.


  
  
# Re-look at the Ungrammaticality Assymetry
  
  
-   Obviously, I failed to introduce any bias in any of the experiments. 
-   Two questions to ask:
    
    -   There is a clear difference between two experiments. Is this difference only about sampling?
    -   Even though introducing a bias failed, there are still people who were biased (either towards grammatical or ungrammatical) regardless of our experiment.

-   These subgroups of participants should behave according to the predictions.

-   What are the predictions?
  
    -   RT-wise: Faster RTs in ungrammatical conditions.
    -   Response-wise: Ungrammaticality Effects, that is a substantial difference between grammatical-sg attractor and grammatical-pl attractor conditions.


  
  
  
  
# Descriptive Stats
  

## Mean Acceptable Responses

```{r labelParticipants accordingly}
# For ungrammatical bias
# using fillers
## lets use 
biases %<>% within(., {
  Bias <- ifelse(bias < cutpoint, "towardsG", 
                 "towardsUng"
  )
})

bias_df <- biases %>% select(subject, Bias)


df_all  %<>% 
  full_join(., 
            bias_df, 
            by = "subject")



towardsG <- df_all %>% filter(Bias == "towardsG")
avg_clean <- list()
avg_clean$resp <- towardsG %>% 
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = TRUE)
  })

avg_clean$rt_correct <- towardsG %>% subset(ResponseCorrect) %>%
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = FALSE)
  })

avg_exp <- avg_clean %>% 
  lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") })
avg_exp$resp$bias <- "Bias Towards Grammatical"
avg_exp$rt_correct$bias <- "Bias Towards Grammatical"
pd <- position_dodge(0.0)
p_avg_resp <- avg_exp$resp %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp <- p_avg_resp + theme_bw()
p_avg_resp_towardsG <- p_avg_resp + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20))


############

towardsUng <- df_all %>% filter(Bias == "towardsUng")
avg_clean2 <- list()
avg_clean2$resp <- towardsUng %>% 
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = TRUE)
  })

avg_clean2$rt_correct <- towardsUng %>% subset(ResponseCorrect) %>%
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = FALSE)
  })

avg_exp2 <- avg_clean2 %>% 
  lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") })
avg_exp2$resp$bias <- "Bias Towards Ungrammatical"
avg_exp2$rt_correct$bias <- "Bias Towards Ungrammatical"
pd <- position_dodge(0.0)
p_avg_resp2 <- avg_exp2$resp %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_avg_resp2 <- p_avg_resp2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_avg_resp2 <- p_avg_resp2 + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp2 <- p_avg_resp2 + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp2 <- p_avg_resp2 + theme_bw()
p_avg_resp_towardsUng <- p_avg_resp2 + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20))


######

avg_clean3 <- list()
avg_clean3$resp <- df_all %>% 
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = response_yes, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = TRUE)
  })

avg_clean3$rt_correct <- df_all %>% subset(ResponseCorrect) %>%
  plyr::ddply(c("experiment"), function(df) {
    df %>% se_cousineau(n_conditions = 4, subject, DV = RT, 
                        group = c("experiment", "grammatical", "attractor_num"), 
                        is_proportion = FALSE)
  })

avg_exp3 <- avg_clean3 %>% 
  lapply(function(df) { df %>% subset(is.na(source) | experiment != "filler") })

p_avg_resp3 <- avg_exp3$resp %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_avg_resp3 <- p_avg_resp3 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_avg_resp3 <- p_avg_resp3 + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp3 <- p_avg_resp3 + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp3 <- p_avg_resp3 + theme_bw()
p_avg_resp_nobias <- p_avg_resp3 + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20)) + facet_wrap(~experiment, labeller = labeller(experiment = c("AgrAttr" = "No Bias (Groups Together)")))

```

```{r plotsResp, fig.width=15}

p_avg_resp_towardsUng +theme(legend.position="none") + facet_wrap(~bias) | p_avg_resp_towardsG +theme(legend.position="none") + ylab("") + theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + facet_wrap(~bias) | p_avg_resp_nobias + ylab("") + theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) 
```



## Mean Reading Times of Correct Responses

```{r preparePlotRT}


pd <- position_dodge(0.0)
p_rt <- avg_exp$rt_correct %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_rt <- p_rt + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_rt <- p_rt + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Mean RT (ms)")
p_rt <- p_rt + theme_bw() + scale_y_continuous( limits = c(700,1200), expand = c(0,0) )
p_rt_towardsG <- p_rt + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20))


p_rt2 <- avg_exp2$rt_correct %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_rt2 <- p_rt2 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_rt2 <- p_rt2 + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Mean RT (ms)")
p_rt2 <- p_rt2 + theme_bw() +  scale_y_continuous( limits = c(700,1200), expand = c(0,0) )
p_rt_towardsUng <- p_rt2 + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20))


p_rt3 <- avg_exp3$rt_correct %>%
  ggplot(aes(grammatical, M, #linetype = attractor_num, 
             color = attractor_num, group = attractor_num)) + 
  geom_point(position = pd) + geom_line(position = pd)

p_rt3 <- p_rt3 + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

# p_avg_resp <- p_avg_resp + geom_line(data = avg_fillers) + 
#                             geom_point(data = avg_fillers) + 

p_rt3 <- p_rt3 + theme( strip.background = element_rect(fill="white") ) +
  theme_bw() + xlab("") + ylab("Mean RT (ms)")
p_rt3 <- p_rt3 + theme_bw() + scale_y_continuous( limits = c(700,1200), expand = c(0,0) )
p_rt_nobias <- p_rt3 + scale_color_discrete(name = "Attractor Number", labels = c("Plural", "Singular")) + 
  scale_x_discrete(labels = c("Grammatical\nSingular Verb", "Ungrammatical\nPlural Verb")) + 
  theme(text = element_text(size = 20)) + facet_wrap(~experiment, labeller = labeller(experiment = c("AgrAttr" = "No Bias (Groups Together)")))

```


```{r plotsRT, fig.width=15}

p_rt_towardsUng +theme(legend.position="none") + facet_wrap(~bias) | p_rt_towardsG + ylab("") + theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + theme(legend.position="none") + facet_wrap(~bias) | p_rt_nobias + ylab("") + theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
```

# Session Info

```{r session-info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info(pkgs = NULL, include_base = FALSE)
```